An institutional approach to attention allocation and venture resource mobilization and acquisition

### 2021-03-15 Manuscript.tex
Finalizing manuscript

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
}

@@

\hypertarget{measures}{%
\subsection{Measures}\label{measures}}

@@

@@

\hypertarget{data}{%
\subsection{Data}\label{data}}

I set aside XXX nonprofit organizations and XXX observations that are missing relevant venture information or preference ranking, resulting in xxx observations in the final sample. All financial statistics are in United States Dollars (USD). ********

@@

The ventures in our sample are nested within countries. To account for such nested (or hierarchical) structure of the data, I opt for a linear mixed effects model to estimate the effects of each resource alone and when it interacts with institutional level of the resource. This helps us account for fixed effects and random effects associated with non-nested grouping factors. Namely, it allows us to take into account the institutional (i.e.~country) effect on venture outcomes and quantify the extent to which differences in outcomes reflect differences in the effects of country-specific features, specifically institutional level capital.

The following equation (formulas) show all the models by outcome category. Of note, I run all the following models with conrols and without controls as robustness check. Control vriables are HCI refering to Human Capital Index and GC refering to Gender composition (i.e.~female percentage in a team).

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  \emph{Participated \textasciitilde{} AHC + (AHC \textbar{} Country) ; AHC = Attention to Human Capital}
\item
  \emph{Participated \textasciitilde{} AHC + (AHC x Ease of finding skilled employees \textbar{} Country)}
\item
  \emph{Participated \textasciitilde{} AFC + (AFC \textbar{} Country) ; AHC = Attention to Financial Capital}
\item
  \emph{Participated \textasciitilde{} AFC + (AFC x Financing of SMEs\textbar{} Country)}\\
\item
  \emph{Participated \textasciitilde{} AFC + (AFC x VC availability \textbar{} Country)}\\
\item
  \emph{Participated \textasciitilde{} AFC + (AFC x Domestic Credit Gaps \textbar{} Country)}\\
\item
  \emph{Participated \textasciitilde{} ASC + (ASC \textbar{} Country) ; ASC = Attention to Social Capital}\\
\item
  \emph{Participated \textasciitilde{} ASC + (ASC x State of cluster development \textbar{} Country)}
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{8}
\tightlist
\item
  \emph{Total employees \textasciitilde{} AHC + (AHC \textbar{} Country)}
\item
  \emph{Total employees \textasciitilde{} AHC + (AHC x Ease of finding skilled employees \textbar{} Country)}
\item
  \emph{Capital Raised \textasciitilde{} AFC + (AFC \textbar{} Country)}
\item
  \emph{Capital Raised \textasciitilde{} AFC + (AFC x Financing of SMEs\textbar{} Country)}
\item
  \emph{Capital Raised \textasciitilde{} AFC + (AFC x VC availability \textbar{} Country)}
\item
  \emph{Capital Raised \textasciitilde{} AFC + (AFC x VC availability \textbar{} Country)}
\item
  \emph{Capital sources \textasciitilde{} ASC + (ASC \textbar{} Country)}\\
\item
  \emph{Capital sources \textasciitilde{} ASC + (ASC x State of cluster development \textbar{} Country)}
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{16}
\tightlist
\item
  \emph{Revenue \textasciitilde{} AHC + (AHC \textbar{} Country)}
\item
  \emph{Revenue \textasciitilde{} AHC + (AHC x Ease of finding skilled employees \textbar{} Country)}
\item
  \emph{Revenue \textasciitilde{} AFC + (AFC \textbar{} Country)}
\item
  \emph{Revenue \textasciitilde{} AFC + (AFC x Financing of SMEs\textbar{} Country)}\\
\item
  \emph{Revenue \textasciitilde{} AFC + (AFC x VC availability \textbar{} Country)}\\
\item
  \emph{Revenue \textasciitilde{} AFC + (AFC x Domestic Credit Gaps \textbar{} Country)}\\
\item
  \emph{Revenue \textasciitilde{} ASC + (ASC \textbar{} Country)}\\
\item
  \emph{Revenue \textasciitilde{} ASC + (ASC x State of cluster development \textbar{} Country)}
\end{enumerate}

@@

\caption{\label{tab:unnamed-chunk-18}Effect of attention to human capital}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\hline
Intercept & -1.54 & 0.08 & -19.82 & 0.000 & -1.46 & 0.08 & -19.18 & 0.000\\
\hline
Attention to Human capital(AHC) & 0.09 & 0.07 & 1.24 & 0.215 & 0.11 & 0.07 & 1.54 & 0.123\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.01 & 0.01 & 1.46 & 0.144 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & 0.24 & 0.06 & 4.17 & 0.000 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level of human capital}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\hline
Intercept & -0.94 & 0.53 & -1.80 & 0.073 & -0.85 & 0.53 & -1.61 & 0.108\\
\hline
AHC & 0.90 & 0.45 & 2.01 & 0.044 & 0.92 & 0.45 & 2.05 & 0.040\\
\hline
Ease of finding skilled employees & -0.13 & 0.12 & -1.11 & 0.269 & -0.14 & 0.12 & -1.14 & 0.253\\
\hline
AHCxEase of finding skilled employees & 0.01 & 0.01 & 1.37 & 0.171 & -0.17 & 0.10 & -1.79 & 0.074\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.24 & 0.06 & 4.06 & 0.000 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & -0.17 & 0.10 & -1.80 & 0.073 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-18}Effect of attention to financial capital}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\hline
Intercept & -1.53 & 0.08 & -19.55 & 0.000 & -1.45 & 0.08 & -18.82 & 0.000\\
\hline
Attention to Financial capital & -0.19 & 0.06 & -3.02 & 0.003 & -0.19 & 0.06 & -3.06 & 0.002\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.01 & 0.01 & 1.39 & 0.165 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & 0.25 & 0.06 & 4.34 & 0.000 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level (SME financing) of financial capital}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\hline
Intercept & -1.43 & 0.43 & -3.35 & 0.001 & -1.35 & 0.43 & -3.11 & 0.002\\
\hline
AFC & -0.19 & 0.29 & -0.66 & 0.509 & -0.21 & 0.29 & -0.74 & 0.460\\
\hline
Financing of SMEs & -0.02 & 0.11 & -0.20 & 0.845 & -0.02 & 0.11 & -0.19 & 0.847\\
\hline
AFCxFinancing of SMEs & 0.01 & 0.01 & 1.30 & 0.193 & 0.00 & 0.07 & 0.05 & 0.959\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.25 & 0.06 & 4.25 & 0.000 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & 0.00 & 0.07 & -0.02 & 0.988 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level (VC) of financial capital}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\hline
Intercept & -1.31 & 0.28 & -4.74 & 0.000 & -1.22 & 0.28 & -4.35 & 0.000\\
\hline
AFC & -0.23 & 0.20 & -1.17 & 0.244 & -0.24 & 0.20 & -1.24 & 0.217\\
\hline
VC Availability & -0.07 & 0.09 & -0.75 & 0.454 & -0.07 & 0.09 & -0.79 & 0.432\\
\hline
AFCxVC Availability & 0.01 & 0.01 & 1.31 & 0.190 & 0.01 & 0.05 & 0.28 & 0.778\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.24 & 0.06 & 4.23 & 0.000 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & 0.01 & 0.05 & 0.22 & 0.824 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\hline
Intercept & -1.46 & 0.13 & -11.62 & 0.000 & -1.37 & 0.13 & -10.93 & 0.000\\
\hline
AFC & -0.20 & 0.10 & -1.91 & 0.056 & -0.21 & 0.10 & -1.99 & 0.047\\
\hline
Domestic Credit Gaps & 0.00 & 0.00 & -0.57 & 0.572 & 0.00 & 0.00 & -0.60 & 0.550\\
\hline
AFCxDomestic Credit Gaps & 0.01 & 0.01 & 1.30 & 0.192 & 0.00 & 0.00 & 0.15 & 0.882\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.25 & 0.06 & 4.24 & 0.000 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & 0.00 & 0.00 & 0.08 & 0.938 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-18}Effect of attention to social capital}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\hline
Intercept & -1.53 & 0.08 & -19.37 & 0.000 & -1.45 & 0.08 & -18.62 & 0.000\\
\hline
Attention to Social capital & 0.12 & 0.07 & 1.79 & 0.073 & 0.11 & 0.07 & 1.69 & 0.091\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.01 & 0.01 & 1.29 & 0.197 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & 0.25 & 0.06 & 4.42 & 0.000 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level of social capital}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\hline
Intercept & -0.89 & 0.41 & -2.16 & 0.031 & -0.78 & 0.42 & -1.87 & 0.061\\
\hline
ASC & 0.06 & 0.35 & 0.19 & 0.852 & 0.06 & 0.35 & 0.18 & 0.860\\
\hline
State of cluster development & -0.16 & 0.10 & -1.52 & 0.128 & -0.17 & 0.11 & -1.56 & 0.119\\
\hline
ASCxState of cluster development & 0.01 & 0.01 & 1.22 & 0.223 & 0.01 & 0.08 & 0.15 & 0.883\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.25 & 0.06 & 4.30 & 0.000 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & 0.01 & 0.08 & 0.16 & 0.876 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-24}Effect on revenues}
\centering
\fontsize{7}{9}\selectfont
\begin{tabular}[t]{l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{3}{c|}{\em{Congruence}} & \multicolumn{3}{c}{\em{AHC only}} \\
\cline{2-4} \cline{5-7}
  & $b$ & SE & $t$ & $b$ & SE & $t$\\
\hline
Intercept & 5,033,422.50 & 8,779,342.42 & 0.57 & 2,061,441.83 & 1,172,119.94 & 1.76\\
\hline
AHC & 12,174,047.87 & 13,178,734.99 & 0.92 & 1,309,266.88 & 2,015,947.62 & 0.65\\
\hline
Ease of finding skilled employees & -677,452.53 & 1,991,735.94 & -0.34 & NA & NA & NA\\
\hline
AHCxEase of finding skilled employees & -2,337,599.95 & 2,803,682.74 & -0.83 & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-24}Effect on revenues}
\centering
\fontsize{7}{9}\selectfont
\begin{tabular}[t]{l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{3}{c|}{\em{Congruence}} & \multicolumn{3}{c}{\em{ASC only}} \\
\cline{2-4} \cline{5-7}
  & $b$ & SE & $t$ & $b$ & SE & $t$\\
\hline
Intercept & 3,743,005.06 & 6,777,362.02 & 0.55 & 2,072,186.10 & 1,151,987.55 & 1.80\\
\hline
ASC & -5,807,873.96 & 17,276,071.97 & -0.34 & -2,440,778.66 & 2,993,083.09 & -0.82\\
\hline
State of cluster development & -401,960.58 & 1,679,258.60 & -0.24 & NA & NA & NA\\
\hline
ASCxState of cluster development & 825,623.52 & 4,199,015.96 & 0.20 & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

>>>>

\abstract{
Early stage entrepreneurs have access to limited resources and must decide what should garner their attention. The literatures on entrepreneurial resources and entrepreneurial attention show mixed results and often do not take into account the institutional context of the venture. I approach the question of entrepreneurial attention from an institutional perspective using the Global Accelerator Learning Initiative Data. In contrast to expectation based on the literature, I find that entrepreneurs do not have to align their attention to resources with the availability of resources in their institutional environment. However, their attention to internal human capital (i.e.~building their own business skills) becomes important if we consider the outcome as being selection to an incubation program to mobilize resources and prepare for long-term resource acquisition. Resource acquisition is a long-term goal and that is why I do not see any effects in the short term. In contrast, selection to an incubation program is a short-term goal that opens the door for the long-term effects and that is how early stage ventures should approach their resource base strategy. Mobilization comes first and acquisition would follow. Thus, the question is not what resources to seek, but when to seek mobilization and when to engage in acquisition of a resource.
}

@@

\hypertarget{data-and-measures}{%
\subsection{Data and Measures}\label{data-and-measures}}

The initial sample consists of 22,928 venture from 73 countries. I set aside nonprofit organizations and observations that are missing relevant venture information or preference ranking, resulting in 15981 observations in the final sample. All financial statistics are in United States Dollars (USD).

@@

Figure 5 shows us the correlation between the venture network (i.e.~total equity sources) and the venture attention level to network by country classification. Similarly, Figure 6 shows us the correlation between the venture's total capital raised and the its attention level to direct funding by country classification.

@@

@@

The ventures in the sample are nested within countries. To account for such nested (or hierarchical) structure of the data, I opt for a linear mixed effects model to estimate the effects of each resource alone and when it interacts with institutional level of the resource. This helps us account for fixed effects and random effects associated with non-nested grouping factors. Namely, it allows us to take into account the institutional (i.e.~country) effect on venture outcomes and quantify the extent to which differences in outcomes reflect differences in the effects of country-specific features, specifically institutional level capital.

The following equations show all the models by outcome category. Of note, I run all the initial models (i.e.~resource mobilization models) with conrols and without controls as robustness check. Control vriables are the Human Capital Index and Gender composition (i.e.~female percentage in a team) that were highlight in the previous section about measures. AHC, AFC, and ASC refer to our key predictors; Attention to Human Capital, Attention to Financial Capital, and Attention to Social Capital respectively.

@@

\[{Participated_i} =  \beta_0 + b AHC_i + Controls_i + \epsilon_i \]

\[{Participated_i} =  \beta_0 + b_1 AHC_i + b_2 AHC_i * Ease of finding skilled employees_c+ Controls_i + \epsilon_i \]
\[{Participated_i} =  \beta_0 + b AFC_i +Controls_i + \epsilon_i \]\\
\[{Participated_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Financing of SMEs_c+ Controls_i + \epsilon_i \]
\[{Participated_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * VC availability_c+ Controls_i + \epsilon_i \]
\[{Participated_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Domestic Credit Gaps_c+ Controls_i + \epsilon_i \]
\[{Participated_i} =  \beta_0 + b ASC_i + Controls_i + \epsilon_i \]
\[{Participated_i} =  \beta_0 + b_1 ASC_i + b_2 ASC_i * State of cluster development_c+ Controls_i + \epsilon_i \]

@@

\[{Total Employees_i} =  \beta_0 + b AHC_i + \epsilon_i \]
\[{Total Employees_i} =  \beta_0 + b_1 AHC_i + b_2 AHC_i * Ease of finding skilled employees_c+ \epsilon_i \]
\[{CapitalRaised_i} =  \beta_0 + b AFC_i + \epsilon_i \]
\[{CapitalRaised_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Financing of SMEs_c + \epsilon_i \]
\[{CapitalRaised_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * VC availability_c + \epsilon_i \]
\[{CapitalRaised_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Domestic Credit Gaps_c + \epsilon_i \]
\[{CapitalSources_i} =  \beta_0 + b ASC_i + \epsilon_i \]
\[{CapitalSources_i} =  \beta_0 + b_1 ASC_i + b_2 ASC_i * State of cluster development_c+ \epsilon_i \]

@@

\[{Revenue_i} =  \beta_0 + b AHC_i + \epsilon_i \]
\[{Revenue_i} =  \beta_0 + b_1 AHC_i + b_2 AHC_i * Ease of finding skilled employees_c+ \epsilon_i \]
\[{Revenue_i} =  \beta_0 + b AFC_i + \epsilon_i \]
\[{Revenue_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Financing of SMEs_c + b_3 AFC_i * VC availability_c + b_4 AFC_i * Domestic Credit Gaps_c + \epsilon_i \]
\[{Revenue_i} =  \beta_0 + b ASC_i + \epsilon_i \]
\[{Revenue_i} =  \beta_0 + b_1 ASC_i + b_2 ASC_i * State of cluster development_c+ \epsilon_i \]

@@

\caption{\label{tab:unnamed-chunk-18}Effect of attention to human capital on likelihood of participation}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\hline
Intercept & -1.54 & 0.08 & -19.82 & 0.000 & -1.46 & 0.08 & -19.18 & 0.000\\
\hline
Attention to Human capital(AHC) & 0.09 & 0.07 & 1.24 & 0.215 & 0.11 & 0.07 & 1.54 & 0.123\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.01 & 0.01 & 1.46 & 0.144 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & 0.24 & 0.06 & 4.17 & 0.000 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level of human capital on likelihood of participation}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\hline
Intercept & -0.94 & 0.53 & -1.80 & 0.073 & -0.85 & 0.53 & -1.61 & 0.108\\
\hline
AHC & 0.90 & 0.45 & 2.01 & 0.044 & 0.92 & 0.45 & 2.05 & 0.040\\
\hline
Ease of finding skilled employees & -0.13 & 0.12 & -1.11 & 0.269 & -0.14 & 0.12 & -1.14 & 0.253\\
\hline
AHCxEase of finding skilled employees & 0.01 & 0.01 & 1.37 & 0.171 & -0.17 & 0.10 & -1.79 & 0.074\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.24 & 0.06 & 4.06 & 0.000 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & -0.17 & 0.10 & -1.80 & 0.073 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-18}Effect of attention to financial capital on likelihood of participation}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\hline
Intercept & -1.53 & 0.08 & -19.55 & 0.000 & -1.45 & 0.08 & -18.82 & 0.000\\
\hline
Attention to Financial capital & -0.19 & 0.06 & -3.02 & 0.003 & -0.19 & 0.06 & -3.06 & 0.002\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.01 & 0.01 & 1.39 & 0.165 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & 0.25 & 0.06 & 4.34 & 0.000 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level (SME financing) of financial capital on likelihood of participation}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\hline
Intercept & -1.43 & 0.43 & -3.35 & 0.001 & -1.35 & 0.43 & -3.11 & 0.002\\
\hline
AFC & -0.19 & 0.29 & -0.66 & 0.509 & -0.21 & 0.29 & -0.74 & 0.460\\
\hline
Financing of SMEs & -0.02 & 0.11 & -0.20 & 0.845 & -0.02 & 0.11 & -0.19 & 0.847\\
\hline
AFCxFinancing of SMEs & 0.01 & 0.01 & 1.30 & 0.193 & 0.00 & 0.07 & 0.05 & 0.959\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.25 & 0.06 & 4.25 & 0.000 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & 0.00 & 0.07 & -0.02 & 0.988 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level (VC) of financial capital on likelihood of participation}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\hline
Intercept & -1.31 & 0.28 & -4.74 & 0.000 & -1.22 & 0.28 & -4.35 & 0.000\\
\hline
AFC & -0.23 & 0.20 & -1.17 & 0.244 & -0.24 & 0.20 & -1.24 & 0.217\\
\hline
VC Availability & -0.07 & 0.09 & -0.75 & 0.454 & -0.07 & 0.09 & -0.79 & 0.432\\
\hline
AFCxVC Availability & 0.01 & 0.01 & 1.31 & 0.190 & 0.01 & 0.05 & 0.28 & 0.778\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.24 & 0.06 & 4.23 & 0.000 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & 0.01 & 0.05 & 0.22 & 0.824 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital on likelihood of participation}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\hline
Intercept & -1.46 & 0.13 & -11.62 & 0.000 & -1.37 & 0.13 & -10.93 & 0.000\\
\hline
AFC & -0.20 & 0.10 & -1.91 & 0.056 & -0.21 & 0.10 & -1.99 & 0.047\\
\hline
Domestic Credit Gaps & 0.00 & 0.00 & -0.57 & 0.572 & 0.00 & 0.00 & -0.60 & 0.550\\
\hline
AFCxDomestic Credit Gaps & 0.01 & 0.01 & 1.30 & 0.192 & 0.00 & 0.00 & 0.15 & 0.882\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.25 & 0.06 & 4.24 & 0.000 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & 0.00 & 0.00 & 0.08 & 0.938 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-18}Effect of attention to social capital on likelihood of participation}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\hline
Intercept & -1.53 & 0.08 & -19.37 & 0.000 & -1.45 & 0.08 & -18.62 & 0.000\\
\hline
Attention to Social capital & 0.12 & 0.07 & 1.79 & 0.073 & 0.11 & 0.07 & 1.69 & 0.091\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.01 & 0.01 & 1.29 & 0.197 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & 0.25 & 0.06 & 4.42 & 0.000 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level of social capital on likelihood of participation}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\hline
Intercept & -0.89 & 0.41 & -2.16 & 0.031 & -0.78 & 0.42 & -1.87 & 0.061\\
\hline
ASC & 0.06 & 0.35 & 0.19 & 0.852 & 0.06 & 0.35 & 0.18 & 0.860\\
\hline
State of cluster development & -0.16 & 0.10 & -1.52 & 0.128 & -0.17 & 0.11 & -1.56 & 0.119\\
\hline
ASCxState of cluster development & 0.01 & 0.01 & 1.22 & 0.223 & 0.01 & 0.08 & 0.15 & 0.883\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.25 & 0.06 & 4.30 & 0.000 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & 0.01 & 0.08 & 0.16 & 0.876 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-24}Effect on revenues}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{3}{c|}{\em{Congruence}} & \multicolumn{3}{c}{\em{AHC only}} \\
\cline{2-4} \cline{5-7}
  & $b$ & SE & $t$ & $b$ & SE & $t$\\
\hline
Intercept & 5,033,422.50 & 8,779,342.42 & 0.57 & 2,061,441.83 & 1,172,119.94 & 1.76\\
\hline
AHC & 12,174,047.87 & 13,178,734.99 & 0.92 & 1,309,266.88 & 2,015,947.62 & 0.65\\
\hline
Ease of finding skilled employees & -677,452.53 & 1,991,735.94 & -0.34 & NA & NA & NA\\
\hline
AHCxEase of finding skilled employees & -2,337,599.95 & 2,803,682.74 & -0.83 & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-24}Effect on revenues}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{3}{c|}{\em{Congruence}} & \multicolumn{3}{c}{\em{ASC only}} \\
\cline{2-4} \cline{5-7}
  & $b$ & SE & $t$ & $b$ & SE & $t$\\
\hline
Intercept & 3,743,005.06 & 6,777,362.02 & 0.55 & 2,072,186.10 & 1,151,987.55 & 1.80\\
\hline
ASC & -5,807,873.96 & 17,276,071.97 & -0.34 & -2,440,778.66 & 2,993,083.09 & -0.82\\
\hline
State of cluster development & -401,960.58 & 1,679,258.60 & -0.24 & NA & NA & NA\\
\hline
ASCxState of cluster development & 825,623.52 & 4,199,015.96 & 0.20 & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

\hypertarget{results-and-discussion}{%
\section{Results and Discussion}\label{results-and-discussion}}
